Dynamic Stochastic Approximation Monte Carlo

### 2018-07-23 papers/histogram/sad.tex
clean up equation and use \gamma_t more consistently

Outside of the energy range $E_L \le E \le E_H$, the weights are ignored
when computing acceptance probabilities, and the weights $w(E_L)$ or
$w(E_H)$ are used instead.  This means that the histogram is \emph{not}
flat in this region, but instead is proportional to the density of
states.  In order to ensure that $w(E) \propto D(E)$, the change in
weight with each visit should be equal to the change in weight at
the border energy $E=E_{H/L}$.
\begin{align}
  w_{t+1}(E)-w_t(E) &= w_{t+1}(E_{H/L}) -w_t(E_{H/L}) \\
    &= e^\gamma w(E_{H/L}) - w(E_{H/L}) \\
    &= (e^\gamma-1) w(E_{H/L})
\end{align}
This ensures that although we visit each energy above $E_H$ or
below $E_L$ only
in proportion to its density of states, the weights at these energies
will approach the entropy as the simulation progresses.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n500}
  \caption{The update factor $\gamma$ for $N=500$ versus iteration for three
    different methods: WL, SAMC, and SAD.
    method.}\label{fig:gamma-vs-t}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n50}
  \caption{The update factor $\gamma$ for $N=50$ versus iteration for three
    different methods: WL, SAMC, and SAD.  This is exciting because we
    have different MC moves (slow, etc).}
\end{figure}

>>>>

Outside of the energy range $E_L \le E \le E_H$, the weights are ignored
when computing acceptance probabilities, and the weights $w(E_L)$ or
$w(E_H)$ are used instead.  This means that the histogram is \emph{not}
flat in this region, but instead is proportional to the density of
states.  In order to ensure that $w(E) \propto D(E)$, the change in
weight with each visit should be equal to the change in weight at
the border energy $E=E_{H/L}$.
\begin{align}
  w_{t+1}(E)-w_t(E) &= w_{t+1}(E_{H/L}) -w_t(E_{H/L}) \\
    &= (e^{\gamma_t}-1) w_t(E_{H/L})
\end{align}
This ensures that although we visit each energy above $E_H$ or
below $E_L$ only
in proportion to its density of states, the weights at these energies
will approach the entropy as the simulation progresses.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n500}
  \caption{The update factor $\gamma_t$ for $N=500$ versus iteration for three
    different methods: WL, SAMC, and SAD.
    method.}\label{fig:gamma-vs-t}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/gamma-n50}
  \caption{The update factor $\gamma_t$ for $N=50$ versus iteration for three
    different methods: WL, SAMC, and SAD.  This is exciting because we
    have different MC moves (slow, etc).}
\end{figure}
